Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard

### 2015-04-11 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Added images to wall construction section.  Images have different heights that is intended.

@@

>>>>

Natural gas and gasoline only

@@

\subsubsection{Natural Gas}

\begin{figure}[p]
	\includegraphics[width=1.0in]{../Figures/GBNG1_P5120006}
	\includegraphics[width=1.0in]{../Figures/GBNG2_P5120024}
	\includegraphics[width=1.0in]{../Figures/GBNG3_P5120048}
	\includegraphics[width=1.0in]{../Figures/GBNG4_P5120086}	
	\includegraphics[width=1.0in]{../Figures/GBNG5_P5120137} \\

	\includegraphics[width=1.0in]{../Figures/GBNG6_P5120160}
	\includegraphics[width=1.0in]{../Figures/GBNG7_P5120172}
	\includegraphics[width=1.0in]{../Figures/GBNG8_P5120196}
	\includegraphics[width=1.0in]{../Figures/GBNG10_P5120251}	
	\includegraphics[width=1.0in]{../Figures/GBNG13_P5120356} \\

	\caption[Photographs of the fire patterns from ten replicate natural gas burner against open wall construction]{Photographs of the fire patterns from ten replicate natural gas burner against open wall construction.}
	\label{NG_Open_Wall}
\end{figure}

\begin{figure}[p]
	\includegraphics[width=1.0in]{../Figures/GBNG14_P5130378}
	\includegraphics[width=1.0in]{../Figures/GBNG15}
	\includegraphics[width=1.0in]{../Figures/GBNG16}
	\includegraphics[width=1.0in]{../Figures/GBNG17_P5130382}	
	\includegraphics[width=1.0in]{../Figures/GBNG18_P5130386} \\

	\includegraphics[width=1.0in]{../Figures/GBNG19_P5130390}
	\includegraphics[width=1.0in]{../Figures/GBNG20_P5130392}
	\includegraphics[width=1.0in]{../Figures/GBNG21_P5130398}
	\includegraphics[width=1.0in]{../Figures/GBNG22_P5130403}	
	\includegraphics[width=1.0in]{../Figures/GBNG23_P5130412} \\

	\caption[Photographs of the fire patterns from ten replicate natural gas burner against closed wall construction]{Photographs of the fire patterns from ten replicate natural gas burner against closed wall construction.}
	\label{NG_Closed_Wall}
\end{figure}

\begin{figure}[p]
	\includegraphics[width=1.0in]{../Figures/GBNG24_IMG_9020}
	\includegraphics[width=1.0in]{../Figures/GBNG25_P5130419}
	\includegraphics[width=1.0in]{../Figures/GBNG26_P5130427}
	\includegraphics[width=1.0in]{../Figures/GBNG27}	
	\includegraphics[width=1.0in]{../Figures/GBNG28_P5130434} \\

	\includegraphics[width=1.0in]{../Figures/GBNG29_P5130436}
	\includegraphics[width=1.0in]{../Figures/GBNG30_P5130445}
	\includegraphics[width=1.0in]{../Figures/GBNG31_P5130449}
	\includegraphics[width=1.0in]{../Figures/GBNG32}	
	\includegraphics[width=1.0in]{../Figures/GBNG33} \\

	\caption[Photographs of the fire patterns from ten replicate natural gas burner against insulated wall construction]{Photographs of the fire patterns from ten replicate natural gas burner against insulated wall construction.}
	\label{NG_Insulated_Wall}
\end{figure}

\subsubsection{Gasoline}

\begin{figure}[p]
	\includegraphics[width=1.0in]{../Figures/GBGAS_23_IMG_6048}
	\includegraphics[width=1.0in]{../Figures/GBGAS_26_IMG_6192}
	\includegraphics[width=1.0in]{../Figures/GBGAS_27_IMG_6210}
	\includegraphics[width=1.0in]{../Figures/GBGAS_28_IMG_6230}	
	\includegraphics[width=1.0in]{../Figures/GBGAS_29_IMG_6250} \\

	\includegraphics[width=1.0in]{../Figures/GBGAS_30_IMG_6269}
	\includegraphics[width=1.0in]{../Figures/GBGAS_31_IMG_6288}
	\includegraphics[width=1.0in]{../Figures/GBGAS_32_IMG_6307}
	\includegraphics[width=1.0in]{../Figures/GBGAS_33_IMG_6326}	
	\includegraphics[width=1.0in]{../Figures/GBGAS_34_IMG_6345} \\

	\caption[Photographs of the fire patterns from ten replicate gasoline burner against open wall construction]{Photographs of the fire patterns from ten replicate gasoline burner against open wall construction.}
	\label{Gas_Open_Wall}
\end{figure}

\begin{figure}[p]
	\includegraphics[width=1.0in]{../Figures/GBGAS_02_IMG_5554}
	\includegraphics[width=1.0in]{../Figures/GBGAS_05_IMG_5635}
	\includegraphics[width=1.0in]{../Figures/GBGAS_06_IMG_5661}
	\includegraphics[width=1.0in]{../Figures/GBGAS_07_IMG_5679}	
	\includegraphics[width=1.0in]{../Figures/GBGAS_08_IMG_5698} \\

	\includegraphics[width=1.0in]{../Figures/GBGAS_09_IMG_5717}
	\includegraphics[width=1.0in]{../Figures/GBGAS_10_IMG_5737}
	\includegraphics[width=1.0in]{../Figures/GBGAS_11_IMG_5756}
	\includegraphics[width=1.0in]{../Figures/GBGAS_12_IMG_5775}	
	\includegraphics[width=1.0in]{../Figures/GBGAS_13_IMG_5794} \\

	\caption[Photographs of the fire patterns from ten replicate gasoline burner against closed wall construction]{Photographs of the fire patterns from ten replicate gasoline burner against closed wall construction.}
	\label{Gas_Closed_Wall}
\end{figure}

\begin{figure}[p]
	\includegraphics[width=1.0in]{../Figures/GBGAS_03_IMG_5575} 
	\includegraphics[width=1.0in]{../Figures/GBGAS_14_IMG_5814}
	\includegraphics[width=1.0in]{../Figures/GBGAS_15_IMG_5835}
	\includegraphics[width=1.0in]{../Figures/GBGAS_16_IMG_5855}
	\includegraphics[width=1.0in]{../Figures/GBGAS_17_IMG_5875}	\\

	\includegraphics[width=1.0in]{../Figures/GBGAS_18_IMG_5895}
	\includegraphics[width=1.0in]{../Figures/GBGAS_19_IMG_5967}
	\includegraphics[width=1.0in]{../Figures/GBGAS_20_IMG_5986}
	\includegraphics[width=1.0in]{../Figures/GBGAS_21_IMG_6006}
	\includegraphics[width=1.0in]{../Figures/GBGAS_22_IMG_6026}	\\

	\caption[Photographs of the fire patterns from ten replicate gasoline burner against insulated wall construction]{Photographs of the fire patterns from ten replicate gasoline burner against insulated wall construction.}
	\label{Gas_Insulated_Wall}
\end{figure}

\subsubsection{Polyurethane Foam}

\begin{figure}[p]
	\includegraphics[width=1.0in]{../Figures/GBPUF1_IMG_9332}
	\includegraphics[width=1.0in]{../Figures/GBPUF2_IMG_9347}
	\includegraphics[width=1.0in]{../Figures/GBPUF3_IMG_9362}
	\includegraphics[width=1.0in]{../Figures/GBPUF4_IMG_9376}	
	\includegraphics[width=1.0in]{../Figures/GBPUF5_IMG_9390} \\

	\includegraphics[width=1.0in]{../Figures/GBPUF6_IMG_9403}
	\includegraphics[width=1.0in]{../Figures/GBPUF7_IMG_9416}
	\includegraphics[width=1.0in]{../Figures/GBPUF8_IMG_9429}
	\includegraphics[width=1.0in]{../Figures/GBPUF9_IMG_9446}	
	\includegraphics[width=1.0in]{../Figures/GBPUF10_IMG_9461} \\

	\caption[Photographs of the fire patterns from ten replicate polyurethane foam burner against open wall construction]{Photographs of the fire patterns from ten replicate polyurethane foam burner against open wall construction.}
	\label{PUF_Open_Wall}
\end{figure}
